Formulating Regional Typologies

### 2023-11-01 regional_typologies.qmd
Updated map

## Agenda
0.  Background Context
1.  Understanding the Regional Typologies
2.  Methodology
3.  Case Studies
4.  Closing Remarks

-----------------------------------------------------------------------

@@

- The concept of "Regional Typology" identifies common characteristics—whether in villages, districts, or special units—that guide the formulation of both planning units and strategy or intervention recommendations.

@@

- The masterplan will include a range of tailored strategies and on-site interventions, reflecting the specific needs of each planning unit.
:::
------------------------------------------------------------------------

@@

|---------------|-------------------------|------------------|---------------|

@@

| 15  | Arable land                                         | Land cover map 2020, MoEF                               | % |

@@

@@

|------------------|------------------|------------------|--------------------|

@@

| **Typology** | **R.3.1 Establishment of Peatland Stewardship Village**                                                                                                                                                                                                               | **R.3.2 Enhancing Livelihood Capacity**                                                                                                          | **R.3.3 Development of Alternative Commodities and Livelihood Sources**                                                             |
|------------------|------------------|------------------|--------------------|
| **1**        | \- Community awareness about the importance of the peat ecosystem, collaborating with district and provincial governments. <br><br> - Activities of the Peatland Stewardship Village aimed at increasing income and creating sources of livelihood for the community. | Conducted in synergy with district/city governments.                                                                                             | Directed at non-agricultural livelihood sources (off-farm). Local industries that exist need support.                               |
| **2**        | Peatland Stewardship Village is executed in an integrated manner in partnership with HTI companies and palm oil plantations. The goal is to enhance community access.                                                                                                 | Strengthening farmers' livelihoods to protect the remaining peat ecosystems. Formulation of alternative livelihood sources.                      | Livelihood sources oriented towards peat-friendly agriculture, mixed plantations combined with non-agricultural livelihood sources. |
| **3**        | Peatland Stewardship Village is oriented towards fire prevention; conducted in an integrated manner in partnership with HTI companies and palm oil plantations.                                                                                                       | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Livelihoods aimed at forest and land fire prevention. | Livelihood sources oriented towards peat-friendly agriculture and plantations combined with fisheries and livestock.                |
| **4**        | Peatland Stewardship Village geared towards fire prevention; enhancing community access to markets and high-economic value commodities.                                                                                                                               | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
| **5**        | Peatland Stewardship Village focused on fire prevention; enhancing community access to markets and commodities of high economic value.                                                                                                                                | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |

>>>>

## Agenda

0.  Background Context
1.  Understanding the Regional Typologies
2.  Methodology
3.  Case Studies
4.  Closing Remarks

@@

-   The concept of "Regional Typology" identifies common characteristics---whether in villages, districts, or special units---that guide the formulation of both planning units and strategy or intervention recommendations.

@@

-   The masterplan will include a range of tailored strategies and on-site interventions, reflecting the specific needs of each planning unit.
:::

@@

|-----|--------------------------------------------------------|---------------------------------------------------------|-----------------|

@@

| 15  | Arable land                                            | Land cover map 2020, MoEF                               | \%              |

@@

![](image/5cluster.png){height="450" fig-align="center"}

@@

|-----|-------------------------------|-----------------------------------------------------------|------------------------------------------------------------------------------|

@@

| **Typology** | **R.3.1 Establishment of Peatland Stewardship Village**                                                                                                                                                                                                               | **R.3.2 Enhancing Livelihood Capacity**                                                                                                          | **R.3.3 Development of Alternative Commodities and Livelihood Sources**                                                             |
|--------------|-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|--------------------------------------------------------------------------------------------------------------------------------------------------|-------------------------------------------------------------------------------------------------------------------------------------|
| **1**        | \- Community awareness about the importance of the peat ecosystem, collaborating with district and provincial governments. <br><br> - Activities of the Peatland Stewardship Village aimed at increasing income and creating sources of livelihood for the community. | Conducted in synergy with district/city governments.                                                                                             | Directed at non-agricultural livelihood sources (off-farm). Local industries that exist need support.                               |
| **2**        | Peatland Stewardship Village is executed in an integrated manner in partnership with HTI companies and palm oil plantations. The goal is to enhance community access.                                                                                                 | Strengthening farmers' livelihoods to protect the remaining peat ecosystems. Formulation of alternative livelihood sources.                      | Livelihood sources oriented towards peat-friendly agriculture, mixed plantations combined with non-agricultural livelihood sources. |
| **3**        | Peatland Stewardship Village is oriented towards fire prevention; conducted in an integrated manner in partnership with HTI companies and palm oil plantations.                                                                                                       | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Livelihoods aimed at forest and land fire prevention. | Livelihood sources oriented towards peat-friendly agriculture and plantations combined with fisheries and livestock.                |
| **4**        | Peatland Stewardship Village geared towards fire prevention; enhancing community access to markets and high-economic value commodities.                                                                                                                               | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
| **5**        | Peatland Stewardship Village focused on fire prevention; enhancing community access to markets and commodities of high economic value.                                                                                                                                | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
